Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-20 transmission.tex
More readable fig 7.1

During November, incidence starts rising, with regional heterogeneity in the timing of when this occurs (see \cref{transmission:fig:backcalc-regions}).
The most explored explanation for this is the emergence of the Alpha variant, which was more transmissible than previous variants and emerged at different times across the country~\autocite{walkerTracking,daviesEstimated,lythgoeLineage}.
There is evidence that when incidence starts increasing is correlated with when the Alpha variant's spread (see \cref{transmission:fig:backcalc-alpha}).
A second peak occurs in late December or early January in all regions; this second peak is larger than the first in all regions except the Northern three (North East, North West, and Yorkshire and the Humber).
\begin{figure}
    \todo[inline]{Make figure backcalc-regions easier to read}
    \includegraphics{transmission/backcalc-regions}
    \caption[Incidence estimated using backcalculation by region]{%
        Incidence proportion for all of England (A) and its component regions.
        Regions are split into broad groupings of three regions each: Northern (B), Midlands (C), and Southern (D).
        Yorkshire and the Humber is labelled as Yorkshire for brevity.
    }
    \label{transmission:fig:backcalc-regions}
\end{figure}
\begin{figure}
    \includegraphics{transmission/backcalc-alpha}
    \caption[Correlation of the emergence of Alpha and minimum incidence.]{%
        x-axis: time that S-gene target failure, a marker of the Alpha variant, is estimated to start increasing from baseline by region among CIS test results; from \textcite[table S3]{walkerTracking}.
        y-axis: posterior median and 95\% CrI of the date of minimum incidence in November or early December in each region.
        Linear regression line shown.
    }
    \label{transmission:fig:backcalc-alpha}
\end{figure}

>>>>

During November, incidence starts rising, with regional heterogeneity in the timing of when this occurs (see \cref{transmission:fig:backcalc-regions}).
The most explored explanation for this is the emergence of the Alpha variant, which was more transmissible than previous variants and emerged at different times across the country~\autocite{walkerTracking,daviesEstimated,lythgoeLineage}.
There is evidence that when incidence starts increasing is correlated with when the Alpha variant's spread (see \cref{transmission:fig:backcalc-alpha}).
A second peak occurs in late December or early January in all regions; this second peak is larger than the first in all regions except the Northern three (North East, North West, and Yorkshire and the Humber).
\begin{figure}
    \includegraphics{transmission/backcalc-regions}
    \caption[Incidence estimated using backcalculation by region]{%
        Incidence proportion for (A) all of England and (B) its component regions.
        Yorkshire and the Humber is labelled Yorkshire for brevity.
    }
    \label{transmission:fig:backcalc-regions}
\end{figure}
\begin{figure}
    \includegraphics{transmission/backcalc-alpha}
    \caption[Correlation of the emergence of Alpha and minimum incidence.]{%
        x-axis: time that S-gene target failure, a marker of the Alpha variant, is estimated to start increasing from baseline by region among CIS test results; from \textcite[table S3]{walkerTracking}.
        y-axis: posterior median and 95\% CrI of the date of minimum incidence in November or early December in each region.
        Linear regression line shown.
    }
    \label{transmission:fig:backcalc-alpha}
\end{figure}
